Considering scale in multilayer animal social networks

### 2020-06-22 paper/manuscript.Rmd
mv drop

>>>>

<!-- habitat+social -->

<!-- drop 
Our results highlight the influence of social, spatial and temporal scale on
multilayer networks. For social scale, we found individuals became more
connected with increasing social distance threshold. Increasing land cover
resolution lead to a decrease in availability of patchy and rare habitats and,

QW: not sure I'd mention 'rare' since there are only 3 habitat types. 
Could you just say 'less common' or even just 'patchy'?

correspondingly, lower connectivity of individuals in these habitats. Temporal
windows highlighted clear periods of increased sociality among individuals.
Finally, increasing number of observations led to a general stabilization in network
metrics. As such, scale is inherently tied to the generation  of multilayer
networks and metrics evaluating them, as well as the individual layers that make
them up.
-->
